\documentclass[]{article}
\RequirePackage{amsmath}
\RequirePackage{amsfonts}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{gensymb}

\setlength{\oddsidemargin}{0in} \setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in} \setlength{\headsep}{0pt}
\setlength{\headheight}{0pt} \setlength{\topmargin}{0in}
\setlength{\textheight}{9.5in}
%\title{\textbf{Essential and Redundant Controls of System \\ \small{Using uncompromised controls, can we restore system suffering malicious control?}}
%\\{Research Update}
%\\{Shamina Hossain}
%\\{11/12/15}}
%\date{}
\begin{document}
\thispagestyle{empty}
%\maketitle

\noindent Taylor K McKenzie\\1017 Adams St SE\\ Albuquerque, NM 87108\\ (509) 430-0031\\ tkmckenzie@gmail.com\\ \\
\today

\subsection*{RAND Corporation}

To Whom It May Concern: \\

I am a Ph.D. candidate in Economics at the University of Oregon pursuing research in Industrial Organization and Applied Econometrics, and I am writing to express my strong interest in the research position at the RAND Corporation. My research has focused on identifying productive capabilities and pricing behavior of firms in network industries with a specific interest in the determinants of those characteristics and how they evolve over time. Further, I am interested in technology's role in productivity growth, especially in the context of regulation and policy intervention, and achieving sustainable growth in the face growing demand. I have a wide range of econometric skills in Bayesian analysis, but also in traditional structural modeling, time-series analysis, and reduced-form econometrics. I enjoy exploring problems that are not only relevant to policy but also challenge me to adapt my existing knowledge to find effective solutions.\\

I look forward to applying what I've learned about traditional and structural modeling and econometrics as well as exploring new topics and methods to contribute to RAND's mission. In addition to conducting various empirical analyses, I have experience acquiring, cleaning, and managing data from many sources. While I am most comfortable working in R, Python, Matlab, and Stata, I have developed in numerous programming languages and am comfortable and willing to learn to work in different frameworks. I also have an extensive history working on interdisciplinary teams and synthesizing findings from many backgrounds to arrive at robust, well-founded results. Finally, I have taught many discussion and lab sections as well as several independent courses at the University of Oregon, an experience which has allowed me to hone my ability to describe topics clearly and effectively. I believe this skill will be very useful in communicating findings to policy-makers and the research community alike.\\

With my previous experience in conducting structural analysis, developing and utilizing a multitude of statistical methods, and working on interdisciplinary teams, I believe I can be a valuable constituent of RAND. I look forward to the possibility of working with experts from many subject areas, having access to and analyzing rich data sets, and contributing to novel solutions needed to help promote growth, opportunity, and sustainability around the world.\\

I have attached all other requested materials, please let me know if there is anything else you need. I appreciate your consideration and look forward to hearing from you.\\\\

\noindent Sincerely,\\

\noindent Taylor McKenzie
\end{document}